%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{A lean and fast online menu for its café and restaurant} % subtitle
{Allegro Cultural Center} % title
{2022} % Date
{Shiraz} % Location
{
  \mitalt{Stack:}
  NextJS \mitdiv ReactJS \mitdiv TailwindCSS \mitdiv Adobe XD \mitdiv Git \mitdiv Cloudflare
  \newline
  The website was designed using Adobe XD to meet the business's preferences for UI content and styling.
  Then to develop a fast , mobile friendly website I uses NextJS to have static site generation feature
  and TailwindCSS to have its mobile-first and utility-first approach.
}

%---------------------------------------------------------
\cventry
{Dynamic reservation and food ordering system for a restaurant} % subtitle
{Boomi Restaurant} % title
{2022} % Date
{Shiraz} % Location
{
  \mitalt{Stack:}
  NextJS \mitdiv ReactJS \mitdiv TailwindCSS \mitdiv Adobe XD \mitdiv Git \mitdiv Vercel
  \newline
  This project has three phases encompass three courses of my university curriculum:
  \newline
  In the final phase, user stories, UML models, database tables, and UI prototypes have been designed
  according to software engineering methods. Then I use NextJS as the framework for both developing UI
  and backend and connect them to database by Sequelize.
}

%---------------------------------------------------------
\cventry
{Personal Portfolio which indicates and investigates my skills and knwoledge} % subtitle
{iMitra} % title
{2021} % Date
{Shiraz} % Location
{
  \mitalt{Stack:}
  NextJS \mitdiv ReactJS \mitdiv CSS3 \mitdiv Adobe XD \mitdiv Git \mitdiv Cloudflare
  \newline
  This portfolio has been rebuilt , redesigned and extended over time .
  First was built with WordPress Elementor and then rebuilt using NextJS, ReactJS and CSS3 .
  To ensure the project was well-documented and to keep a clear record of the development process
  I committed all changes to Git .
}

%---------------------------------------------------------
\cventry
{Analyzing information management system's concepts} % subtitle
{Boomi restaurant (phase 2)} % title
{2021} % Date
{Shiraz} % Location
{
  \mitalt{Stack:}
  Visual Paradigm
  \newline
  The second phase centered around importance of data in modern industry competition.
  Containing how to make a manager accompany with an information system while also ensuring
  the security of these valuable assets.
}

%---------------------------------------------------------
\cventry
{Analyzing eBusiness concepts} % subtitle
{Boomi restaurant (phase 1)} % title
{2021} % Date
{Shiraz} % Location
{
  \mitalt{Stack:}
  Visual Paradigm
  \newline
  The overall objective of the first phase was to offer an e-business system to a local company
  in order to help them stay competitive in their industry. So focused on analyzing e-business concepts
  includes who are customers and what are the values represented to them, extracting customers' and employers' needs,
  specifying the service and marketing.
}

%---------------------------------------------------------
\cventry
{Personal Portfolio} % subtitle
{iMitra (Old website)} % title
{2020} % Date
{Shiraz} % Location
{
  \mitalt{Stack:}
  WordPress \mitdiv Elementor \mitdiv CSS3
}

%---------------------------------------------------------
\cventry
{Online shop for a local tailoring brand in Shiraz} % subtitle
{Fatima Collection} % title
{2020} % Date
{Shiraz} % Location
{
  \mitalt{Stack:}
  WordPress \mitdiv Elementor \mitdiv CSS3 \mitdiv Adobe XD \mitdiv WooCommerce
  \newline
  I designed UI with brand's styling theme and preferences , and used WordPress Elementor to give them all an online shop needs , from introduction and contact with customers to sales and inventory management.
}

%---------------------------------------------------------
% \cventry
% {subtitle} % subtitle
% {title} % title
% {2021} % Date
% {Shiraz} % Location
% {
%   \mitalt{Stack:}
%   XXX \mitdiv YYY 
%   \newline
%   DESC
% }

% ---------------------------------------------------------
\end{cventries}
