\section{Projects}
%
\datedexperience{Boomi restaurant}{2022} 
\explanation{Dynamic reservation and food ordering system for a restaurant} 
\explanationdetail{\coloredbullet\ %
\textbf{\emph{Tech:}} NextJS \cpshalf ReactJS \cpshalf TailwindCSS \cpshalf Adobe XD  Vercel \cpshalf Git \cpshalf Visual Paradigm

This project has three phases encompass three courses of my university curriculum:
1.Electronic Business 
The overall objective of the first phase was to offering an e-business system to a local company in order to help them stay competitive in their industry. To achieve this goal, I came up with the idea of a dynamic reservation/ordering system for restaurants.
So this phase focused on analysing e-business concepts includes: who are customers and what are the values represented to them , extracting customers' and employers' needs , specifying the service and finally marketing.

2.Information management System 
The second phase centered around importance of data in modern industry competition. Containing how to make a manager accompany with an information system while also ensuring the security of these valuable assets.

3.Final bachelor project
In the final phase, I took on the role of a software developer and built an application step by step. This involved designing user stories, UML models, database tables, and UI prototypes. Then I decide to use NextJS as the framework for both developing UI and backend and connect them to database by Sequelize . 
}
%
% Blank lines result in extra space!
%
\datedexperience{Allegro cultural center}{2021 -- 2022} 
\explanation{A lean and fast online menu for its café} 
\explanationdetail{\coloredbullet\ %
To facilitate staff's work and delight customers , that can be accessable by scanning a QR code on café's tables .
The website was designed using Adobe XD to meet the business's preferences for UI content and styling. Then to develop a fast , mobile friendly website I uses NextJS to have static site generation feature and TailwindCSS to have its mobile-first and utility-first approach.
Using :: NextJS , ReactJS , TailwindCSS , Adobe XD , Git , Cloudflare
}
%
% Blank lines result in extra space!
%
\datedexperience{iMitra}{2021} 
\explanation{Portfolio} 
\explanationdetail{\coloredbullet\ %
I wanted to have a personal website to not only indicate myself , but also investigate my studies and knowledge gained from different course. Therefore this portfolio has been rebuilt , redesigned and extended over time . First was built with WordPress Elementor and then rebuilt using NextJS, ReactJS and CSS3 . To ensure the project was well-documented and to keep a clear record of the development processI committed all changes to Git .
Using: NextJS , ReactJS , CSS3 , Cloudflare , Git ,Adobe XD , WordPress , Elementor
}
%
% Blank lines result in extra space!
%
\datedexperience{iMitra}{2020} 
\explanation{Online shop for a local tailoring brand in Shiraz} 
\explanationdetail{\coloredbullet\ %
I designed UI with brand's styling theme and preferences , and used WordPress Elementor to give them all an online shop needs , from introduction and contact with customers to sales and inventory management .
Using : WordPress , Elementor , WooCommerce
}
%
